Concurrent Priority Queues

### 2014-03-24 presentation/presentation.tex
Reference section title in frame headers
Fine-grained locking section

\usepackage{acronym}
\usepackage[backend=bibtex]{biblatex}
\usepackage{default}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{lmodern}
\usepackage{textcomp}

@@

% --------------------------------------------------------------------------------------------------
\section{Introduction}
% --------------------------------------------------------------------------------------------------

\begin{frame}[fragile,allowframebreaks]{Introduction}
\acp{PQ}:

@@

\begin{frame}[allowframebreaks]{Terminology}
\begin{itemize}
\item Safety conditions: nothing bad has happened yet
    \begin{itemize}
    \item \emph{Linearizability}: operations appear to take effect at a single point in time, the linearization point
    \item \emph{Quiescent consistency}: in a period of quiescence, semantics equivalent to some sequential ordering
    \item And others, i.e. \emph{sequential consistency}, \emph{serializability}
    \end{itemize}

@@

% --------------------------------------------------------------------------------------------------
\section{Related Work}
% --------------------------------------------------------------------------------------------------

\begin{frame}{Related Work}
\begin{itemize}
\item Non-standard synchronization primitives
    \begin{itemize}
    \item \citeauthor{liu2012lock}: Array-based PQ with \lstinline|ExtractMany|
    \item \citeauthor{israeli1993efficient}: Wait-free PQ
    \end{itemize}

@@

% --------------------------------------------------------------------------------------------------
\section{Concepts and Definitions}
% --------------------------------------------------------------------------------------------------

% --------------------------------------------------------------------------------------------------
\section{Fine-grained Locking Heaps}
% --------------------------------------------------------------------------------------------------

% --------------------------------------------------------------------------------------------------
\section{Lock-free Priority Queues}
% --------------------------------------------------------------------------------------------------

% --------------------------------------------------------------------------------------------------
\section{Relaxed Priority Queues}
% --------------------------------------------------------------------------------------------------

% --------------------------------------------------------------------------------------------------
\section{Conclusion}
% --------------------------------------------------------------------------------------------------

% --------------------------------------------------------------------------------------------------
\section{References}
% --------------------------------------------------------------------------------------------------

\begin{frame}[allowframebreaks]{References}
\printbibliography
\end{frame}

>>>>

\usepackage{acronym}
\usepackage[backend=bibtex]{biblatex}
\usepackage{default}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{lmodern}
\usepackage{nameref}
\usepackage{textcomp}

@@

% --------------------------------------------------------------------------------------------------
\section{Introduction} \label{sec:intro}
% --------------------------------------------------------------------------------------------------

\begin{frame}[fragile,allowframebreaks]{\nameref{sec:intro}}
\acp{PQ}:

@@

\begin{frame}[allowframebreaks]{Concepts and Definitions}
\begin{itemize}
\item Safety conditions: nothing bad has happened yet
    \begin{itemize}
    \item \emph{Linearizability}: operations appear to take effect at a single point in time, the linearization point
    \item \emph{Quiescent consistency}: in a period of quiescence, semantics equivalent to some sequential ordering
    \item And others, i.e. \emph{sequential consistency}, \emph{serializability}
    \end{itemize}

@@

% --------------------------------------------------------------------------------------------------
\section{Related Work} \label{sec:related}
% --------------------------------------------------------------------------------------------------

\begin{frame}{\nameref{sec:related}}
\begin{itemize}
\item Non-standard synchronization primitives
    \begin{itemize}
    \item \citeauthor{liu2012lock}: Array-based PQ with \lstinline|ExtractMany|
    \item \citeauthor{israeli1993efficient}: Wait-free PQ
    \end{itemize}

@@

% --------------------------------------------------------------------------------------------------
\section{Fine-grained Locking Heaps} \label{sec:locking}
% --------------------------------------------------------------------------------------------------

\begin{frame}{\nameref{sec:locking}}
\begin{itemize}
\item Naive PQ parallelization: single global lock \textrightarrow ~ sequential bottleneck
\item A first improvement: fine-grained locking using a lock per node
\item \fullcite{hunt1996efficient}
\end{itemize}
\end{frame}

\begin{frame}{\nameref{sec:locking}}
\framesubtitle{Innovations}

\begin{itemize}
\item One lock per node, \emph{but} additionally a global lock protecting the heap's
      \lstinline|size| variable
\item Insertions bottom-up, deletions top-down to reduce contention
\item Successive insertions take disjoint paths towards the root
\end{itemize}
\end{frame}

\begin{frame}{\nameref{sec:locking}}
\framesubtitle{Limitations}

\begin{itemize}
\item A global lock remains
\item Heap is statically allocated
\item Frequent complex heap reorganization
\item Disjoint-access breaks down at high traffic levels
\item Inherent PQ bottleneck at the minimal node
\item Benchmarks show only limited scalability up to a low thread count
\end{itemize}
\end{frame}

% --------------------------------------------------------------------------------------------------
\section{Lock-free Priority Queues} \label{sec:lockfree}
% --------------------------------------------------------------------------------------------------

\begin{frame}{\nameref{sec:lockfree}}

% --------------------------------------------------------------------------------------------------
\section{Relaxed Priority Queues} \label{sec:relaxed}
% --------------------------------------------------------------------------------------------------

\begin{frame}{\nameref{sec:relaxed}}

% --------------------------------------------------------------------------------------------------
\section{Conclusion} \label{sec:conclusion}
% --------------------------------------------------------------------------------------------------

\begin{frame}{\nameref{sec:conclusion}}

% --------------------------------------------------------------------------------------------------
\section{References} \label{sec:references}
% --------------------------------------------------------------------------------------------------

\begin{frame}[allowframebreaks]{\nameref{sec:references}}
\printbibliography
\end{frame}
